---
title: "PRIZE DRAW for the YCE Fertility Survey"
output: pdf_document
date: "Updated: `r Sys.Date()`"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```


## Selection of YCE Fertility participants for the prizes

All participants who completed the the online survey on Fertility Preservation run by YCE were invited to follow a separate link and provide their contact if they wished to be included in the prize draw for 1 of the 20 gift vouchers valued at 25 euros.

This is the replicable code on how the winners were selected.
Total number of eligible emails submitted was 591, for odds of `r round(20/591, 2)`.

```{r}
prize_raw_data <- read_csv("prize_draw.csv") %>% # raw data extracted for the prize draw
  select_all(tolower) %>%
  rename_with(~gsub("0", "_", .x, fixed = TRUE)) %>% # this is just to clean up the file
  rename_with(~gsub("[", "_", .x, fixed = TRUE)) %>%
  rename_with(~gsub("]", "", .x, fixed = TRUE)) %>%
  filter(prize_draw == 1) # this is to  filter out those who consented

emails <- prize_raw_data %>% # subset and filter only the variable of interest i.e. email
  dplyr::select(prize_email)

set.seed(12345) #set seed to make this reproducible

prize <- sample_n(emails, 20) # randomly select the 20 lucky winners

write_csv(prize, "~/Desktop/prize_emails.csv")
```

Winners will be contacted via email to confirm their acceptance of the prize.
Upon that, YCE will provide them with a digital voucher to their preferred email address.

If no response is received after 2 weeks, YCE will conduct another draw for the remaining prizes.