---
title: "Onco-Fertility preservation: Progress report"
output: pdf_document
author: "Youth Cancer Europe"
date: "`r Sys.Date()`"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(readr)
library(here)
library(psych)
library(english)
library(stringr)
library(tableone)
library(kableExtra)
library(patchwork)
library(scales)
library(ggridges)
library(plotly)
library(patchwork)
library(haven)
```

```{r data, echo=FALSE, message=FALSE, warning=FALSE}
# Read in the clean csv file
raw_data <- read_csv("results.csv")

raw_data$startdate<-as.Date(raw_data$startdate, '%Y-%m-%d')

data <- raw_data %>%
  select_all(tolower) %>%
  rename_with(~gsub("0", "_", .x, fixed = TRUE)) %>%
  rename_with(~gsub("[", "_", .x, fixed = TRUE)) %>%
  rename_with(~gsub("]", "", .x, fixed = TRUE)) %>%
  filter(consent == 1) %>%
  filter(check == 4)

data$startdate<-as.Date(data$startdate, '%Y-%m-%d')## Keep just day, month, year
```

## Literature overview

* We conducted a thorough literature review; from scientific publications to gray literature and clinical guidelines available. The process was facilitated by Zotero, an open source reference manager.

* We developed a better understanding of the needs for patient support, and impact of fertility-related issues on patients' quality of life

* We pinpointed the need to address the issues of fertility preservation from both sides: the patients' side and healthcare professional


## Online Survey 

* Established an Open Science Framework page for the project - please consult [**here**](https://osf.io/sr37b/)
  * The project site contains a detailed description of the survey construction
  
* Had an Expert panel consultation including members from the European Society of Human Reproduction and Embryology (ESHRE) and the University of Edinburgh

* Purchased licence for Lime Survey

* Signed GDPR data protection agreement with Lime Survey (to secure anonymity of participants)

* Finalized the survey protocol and started study recruitment - see the progress below:


  * Number of participants who completed the survey to date: `r raw_data %>% filter(lastpage %in% c(9:10)) %>% nrow()` or `r round((raw_data %>% filter(lastpage %in% c(9:10)) %>% nrow())/(data %>% nrow)*100,1)`% of those who consented.

\newpage 

### Survey entry point

Participants have reported that they most commonly heard about the survey from the following sources:

```{r, echo=FALSE, message=FALSE, warning=FALSE}
data %>%
  dplyr::select(entry) %>%
  group_by(entry) %>%
  drop_na() %>%
  count() %>%
  ungroup() %>%
  mutate(sum = sum(n),
         prop = n/sum*100) %>%
  mutate(entry = as.factor(entry),
         entry = fct_reorder(entry, prop)) %>%
  ggplot(aes(x = prop, y = entry, fill = entry)) + 
  geom_col() + 
  geom_text(aes(label = paste0("N = ", n), x = prop+5)) +
  labs(title = " ", 
       x = "Proportion (%)",
       y = " ") + 
  xlim(0, 100) +
  theme_classic(base_size = 13) +
  theme(legend.position = "none",
        strip.text = element_text(face = 'bold'),
        panel.grid.major.x = element_line()) +
  scale_y_discrete(breaks = c("1", "2", "3", "4", "5", "6", "7", "8",
                              "9", "10"),
                   labels = c("Facebook",
                              "Instagram",
                              "Twitter",
                              "LinkedIn",
                              "Other social media",
                              "YCE Newsletter",
                              "Email",
                              "Patient org.",
                              "Friend",
                              "Other"))
```

\newpage 

### Nationalities represented

To date, participants have been recruited from the following countries. *NB*: The codes are ISO-3 country codes; [**source**](https://www.iban.com/country-codes). Targeted recruitment of nationally-based cancer charities will help us recruit a diverse sample.

```{r, echo=FALSE, message=FALSE, warning=FALSE}
data %>%
  dplyr::select(dem_nationality) %>%
  drop_na() %>%
  group_by(dem_nationality) %>%
  count() %>%
  ungroup() %>%
  mutate(sum = sum(n),
         prop = n/sum,
         prop = round(prop, 2)) %>%
  dplyr::select(-sum) %>%
  kable(col.names = c("Country code", "N", "Proportion")) %>%
  kable_styling("hover", full_width = FALSE, latex_options = "HOLD_position")
```

## Qualitative interview study

* Literature review done
* Held discussions on slight pivoting in aim from fertility preservation services to family planning
* The study protocol has been finalized: objectives, participant selection, general information to be passed to the participants
* Information sheet and informed consent reviewed by YCE legal counsel 
* Currently developing the interview guide
* In the process of applying for ethical approval

