---
title: "YCE Fertility preservation: Survey recruitment progress"
output: pdf_document
date: "Last update: `r Sys.Date()`"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(readr)
library(here)
library(psych)
library(english)
library(stringr)
library(tableone)
library(kableExtra)
library(patchwork)
library(scales)
library(ggridges)
library(plotly)
library(patchwork)
library(haven)
```

```{r data, echo=FALSE, message=FALSE, warning=FALSE}
# Read in the clean csv file
raw_data <- read_csv("results.csv")

raw_data$startdate<-as.Date(raw_data$startdate, '%Y-%m-%d')

data <- raw_data %>%
  select_all(tolower) %>%
  rename_with(~gsub("0", "_", .x, fixed = TRUE)) %>%
  rename_with(~gsub("[", "_", .x, fixed = TRUE)) %>%
  rename_with(~gsub("]", "", .x, fixed = TRUE)) %>%
  filter(consent == 1) %>%
  filter(check == 4)

data$startdate<-as.Date(data$startdate, '%Y-%m-%d')## Keep just day, month, year
```

* This update covers the period between `r min(raw_data$startdate, na.rm = TRUE)` and `r max(raw_data$startdate, na.rm=TRUE)`.

* Visits to the front page of the survey: `r nrow(raw_data)`.

* Number of participants who consented to participate: `r data %>% nrow()`
<!-- `r sum(raw_data$consent, na.rm = TRUE) - raw_data %>% filter(check != 4) %>% nrow()`. -->

* Number of participants who completed the survey: `r raw_data %>% filter(lastpage %in% c(9:10)) %>% nrow()` or `r round((raw_data %>% filter(lastpage %in% c(9:10)) %>% nrow())/(data %>% nrow)*100,1)`% of those who consented.

## Entry point

Participants have reported that they most commonly heard about the survey from the following sources:

```{r, echo=FALSE, message=FALSE, warning=FALSE}
data %>%
  dplyr::select(entry) %>%
  group_by(entry) %>%
  drop_na() %>%
  count() %>%
  ungroup() %>%
  mutate(sum = sum(n),
         prop = n/sum*100) %>%
  mutate(entry = as.factor(entry),
         entry = fct_reorder(entry, prop)) %>%
  ggplot(aes(x = prop, y = entry, fill = entry)) + 
  geom_col() + 
  geom_text(aes(label = paste0("N = ", n), x = prop+5)) +
  labs(title = " ", 
       x = "Proportion (%)",
       y = " ") + 
  xlim(0, 100) +
  theme_classic(base_size = 13) +
  theme(legend.position = "none",
        strip.text = element_text(face = 'bold'),
        panel.grid.major.x = element_line()) +
  scale_y_discrete(breaks = c("1", "2", "3", "4", "5", "6", "7", "8",
                              "9", "10"),
                   labels = c("Facebook",
                              "Instagram",
                              "Twitter",
                              "LinkedIn",
                              "Other social media",
                              "YCE Newsletter",
                              "Email",
                              "Patient org.",
                              "Friend",
                              "Other"))
```

\newpage 

## Nationalities represented

To date, participants have been recruited from the following countries. NB: The codes are ISO-3 country codes; [source](https://www.iban.com/country-codes).

```{r, echo=FALSE, message=FALSE, warning=FALSE}
data %>%
  dplyr::select(dem_nationality) %>%
  drop_na() %>%
  group_by(dem_nationality) %>%
  count() %>%
  ungroup() %>%
  mutate(sum = sum(n),
         prop = n/sum,
         prop = round(prop, 2)) %>%
  dplyr::select(-sum) %>%
  kable(col.names = c("Country code", "N", "Proportion")) %>%
  kable_styling("hover", full_width = FALSE, latex_options = "HOLD_position")
```

## Sex distribution

* 1 = Male
* 2 = Female
* 3 = Other

```{r, echo=FALSE, message=FALSE, warning=FALSE}
data %>%
  dplyr::select(dem_sex) %>%
  drop_na() %>%
  group_by(dem_sex) %>%
  count() %>%
  ungroup() %>%
  mutate(sum = sum(n),
         prop = n/sum,
         prop = round(prop, 2)) %>%
  dplyr::select(-sum) %>%
  kable(col.names = c("Sex", "N", "Proportion")) %>%
  kable_styling("hover", full_width = FALSE, latex_options = "HOLD_position")
```


This document was prepared by UK - [reach me with any questions/comments](mailto:dr.urska.kosir@gmail.com)!